Stack Safety as a Security Property

### 2020-07-09 main.tex
Abstract

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\bcp{Hey, we should have an abstract \ldots}
\end{abstract}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
What is stack safety? Numerous mechanisms have been proposed to guard
against attacks that corrupt the call stacks of running programs, and many
others rely on a protected stack as an assumption to provide higher level
guarantees\bcp{this is a good point, but we don't pick it up anywhere in the
  paper, do we?}, a clear and precise definition of stack safety is missing
from the literature.

We propose a formal definition of stack safety phrased in the technical
terminology of language-based security---as a combination of a
confidentiality property (callees should not be able to read their caller's
stack frames) and an integrity property (callees should not corrupt their
caller's stack frames or control state).
  %
We show how these properties are enforced or approximated by a range of
existing stack protection mechanisms\bcp{that is not exactly what we do,
  though.  Let's (re)write the contributions first.} and discuss some useful
stronger and weaker variants.  \bcp{should we mention stktokens here?}
\end{abstract}
